The resurgence of the linear optics \sihui{quantum} interferometer --- recent advances \& applications

### 2018-01-06 paper.tex
Revision to Section 9.

\title{The resurgence of the linear optics interferometer --- recent advances \& applications}

@@

The promises offered by linear optics have spearheaded many technical advancements. One of the major successes for linear optics is the paradigm shift from bulk optics to integrated photonics \cite{bib:Meany15}. The advantage of using such integrated photonics over bulk optics is that it is more stable against phase fluctuations, and miniaturized. This has increased the scalability of optical implementations of quantum information protocols. Furthermore, it is now possible to have single-photon sources and detectors together with linear-optical networks on a silica chip \cite{bib:Sprengers11, bib:Silverstone14}. Having all components on chip reduces coupling losses which would be crucial for fault-tolerance \cite{bib:Li15}.

@@

\begin{figure}[!htb]
\centering
\includegraphics[width=0.4\columnwidth]{reck}
\caption{Efficient decomposition of arbitrary linear optics networks into a sequence of beamsplitters and phase-shifters.} \label{fig:Reck}	
\end{figure}

@@

Broadly speaking, there are two main classes of photodetectors: non-photon-number-resolving (also referred to as bucket, or on/off) detectors, and photon-number-resolving (PNR) detectors. As the names suggest, non-PNR detectors only detect the presence or absence of photons in an incident beam, while PNR detectors are able to measure its number of photons. The outcomes of a PNR detector are described by the measurement projectors,
\begin{align}
\hat\Pi_n &= \ket{n}\bra{n}, \ n=0,1,\ldots \ ,
\end{align}
while those of the non-photon-number-resolving detectors are given by
\begin{align}
\hat\Pi_\text{off} = \hat\Pi_0, \ {\rm and} \ \hat\Pi_\text{on} = \hat{I} - \hat\Pi_\text{on}\ .
\end{align}
Detailed reviews have been written about these detectors \cite{bib:Hadfield09,bib:Eisaman11}, so we shall only outline a few important examples.

A common example of a non-PNR detector is the avalanche photodiode (APD). These devices are made up of semiconductor material, usually silicon, which generate an electron that quickly generates a cascade of electrons. This avalanche of electrons generate a current that can be measured. APDs are affordable, offer low dark count rates with reasonable efficiency, and can be made to operate in a broad spectrum of wavelengths.
% A downside to using APD is their deadtime. This is a period of time 
%following an avalanche during which the avalanche is stopped by a 
%quenching circuit to reset the APD. No photons can be detected during the 
%deadtime and contributes to photon loss in an APD.
Superconducting nanowire single-photon detector (SNSPD) is another  type of non-PNR detector. This detector operates in its superconducting phase just below the critical density, and it phase changes back to normal when a photon is absorbed. This causes a spike in current around it, which, when detected, would indicate the absorption of the photon.

@@

@@

\subsection{Linear optical quantum computation (LOQC)}\label{sec:LOQC}
The advancements in linear optics have opened up avenues for implementation. One of the key requirements is nonlinear couplings between the different optical modes. Photons do not naturally interact with one another so some careful engineering is needed to achieve this coupling. Methods used include measurements and feedforwarding \cite{bib:KLM01}, and photon-atom interactions \cite{bib:Brod16}. The former requires non-deterministic operations, which succeed only part of the time and have to be repeated. This can be challenging given the limited resources to begin with. Comprehensive reviews have been written previously to cover this topic \cite{bib:JW12,bib:Kok05}, hence we will focus on recent advances.

@@

}
\section{Optical switching}

@@

%% `Elsevier LaTeX' style
\bibliographystyle{elsarticle-num}
%%%%%%%%%%%%%%%%%%%%%%%
\bibliography{paper}

>>>>

\title{The resurgence of the linear optics \sihui{quantum} interferometer --- recent advances \& applications}

@@

The promises offered by linear optics have spearheaded many \sihui{scientific and} technical advancements. One of the major successes for linear optics is \sihui{the detection of gravitational waves by the LIGO experiments based on the Michelson interferometer \cite{bib:LIGO2015}. Another is} the paradigm shift from bulk optics to integrated photonics \cite{bib:Meany15}. The advantage of using such integrated photonics over bulk optics is that it is more stable against phase fluctuations, and miniaturized. This has increased the scalability of optical implementations of quantum information protocols. Furthermore, it is now possible to have single-photon sources and detectors together with linear-optical networks on a silica chip \cite{bib:Sprengers11, bib:Silverstone14}. Having all components on chip reduces coupling losses which would be crucial for fault-tolerance \cite{bib:Li15}.

@@

\begin{figure}[!htb]
\centering
\includegraphics[width=0.4\columnwidth]{reck}
\caption{Efficient decomposition of arbitrary linear optics networks into a sequence of beamsplitters and phase-shifters. \sihui{This setup describes a generalized multi-port Mach-Zehnder interferometer}} \label{fig:Reck}	
\end{figure}

@@

Broadly speaking, there are two main classes of photodetectors: non-photon-number-resolving (also referred to as bucket, or on/off) detectors, and photon-number-resolving (PNR) detectors. As the names suggest, non-PNR detectors only detect the presence or absence of photons in an incident beam, while PNR detectors are able to measure its number of photons. The outcomes of a PNR detector are described by the measurement projectors,
\begin{align}
\hat\Pi_n &= \ket{n}\bra{n}, \ n=0,1,\ldots \ ,
\end{align}
while those of the non-photon-number-resolving detectors are given by
\begin{align}
\hat\Pi_\text{off} = \hat\Pi_0, \ {\rm and} \ \hat\Pi_\text{on} = \hat{I} - \hat\Pi_\text{on}\ .
\end{align}
\sihui{Theoretical modeling of these photodetectors can be made to include realistic effects such as detector finite efficiency, finite-number resolution, dark counts, and crosstalk. These effects are typically described as projections onto mixed states \cite{bib:BARNETT1998}, and their outcomes are represented by positive-operator valued measures. Such modeling allows us to analyze these realistic effects on various quantum information protocols, see for {\it e.g.~}\cite{bib:Ozdemir2001,bib:Sperling2014,bib:Tan2016}.}

\sihui{There are many different types of photodetectors. Detailed reviews have been written about \sihui{them} \cite{bib:Hadfield09,bib:Eisaman11}, so we shall only outline a few important examples. }A common example of a non-PNR detector is the avalanche photodiode (APD). These devices are made up of semiconductor material, usually silicon, which generate an electron that quickly generates a cascade of electrons. This avalanche of electrons generate a current that can be measured. APDs are affordable, offer low dark count rates with reasonable efficiency, and can be made to operate in a broad spectrum of wavelengths.
% A downside to using APD is their deadtime. This is a period of time 
%following an avalanche during which the avalanche is stopped by a 
%quenching circuit to reset the APD. No photons can be detected during the 
%deadtime and contributes to photon loss in an APD.
Superconducting nanowire single-photon detector (SNSPD) is another  type of non-PNR detector. This detector operates in its superconducting phase just below the critical density, and it phase changes back to normal when a photon is absorbed. This causes a spike in current around it, which, when detected, would indicate the absorption of the photon.

@@

\section{Optical switching}

@@

\subsection{Linear optical quantum computation (LOQC)}\label{sec:LOQC}
The advancements in linear optics have opened up avenues for implementation. One of the key requirements is nonlinear couplings between the different optical modes. Photons do not naturally interact with one another so some careful engineering is needed to achieve this coupling. Methods used include measurements and feedforwarding \cite{bib:KLM01}, and photon-atom interactions \cite{bib:Brod16}. The former requires non-deterministic operations, which succeed only part of the time and have to be repeated. This can be challenging given the limited resources to begin with. \sihui{Various linear-optical implementations of two-qubit gates important for approximately universal quantum computation are listed in Ref.~\cite{bib:Bartkowiak2010}, and comprehensive reviews have been written previously to cover this topic \cite{bib:JW12,bib:Kok05}, hence we will focus on recent advances.}

@@

}

@@

%% `Elsevier LaTeX' style
\bibliographystyle{elsarticle-num}

%%%%%%%%%%%%%%%%%%%%%%%
\bibliography{paper}
